\bfseries\LARGE\singlespacing{Transmission of airborne respiratory infections with and without air cleaners in a Swiss school during non-pandemic conditions: A modeling study of epidemiological, environmental, and molecular data}

### 2023-06-22 doc/paper/manuscript.tex

\begin{table}[!htpb]
    \centering
    \caption{Overview of the study population, number of COVID-19 cases, and person-days of absences.}
    \label{tab:cases-overview-school}
    \footnotesize
    \begin{tabular}{l r r r}
    \toprule
         &  School 1 & School 2 & Total \\ \midrule 
        \textbf{Students} & \textbf{52 (58\%)} & \textbf{38 (42\%)} & \textbf{90 (100\%)} \\
        \emph{Gender} \\
        $\drsh$ Female & 20 (38\%) & 19 (50\%) & 39 (\hphantom{0}43\%) \\
        $\drsh$ Male & 32 (62\%) & 19 (50\%) & 51 (\hphantom{0}57\%) \\
        \emph{Vaccination status} \\
        $\drsh$ Vaccinated & 16 (31\%) & 11 (29\%) & 27 (\hphantom{0}30\%) \\
        $\drsh$ Not vaccinated & 36 (69\%) & 27 (71\%) & 63 (\hphantom{0}70\%) \\
        \emph{Recovery status} \\
        $\drsh$ Recovered last year & 25 (48\%) & 9 (24\%) & 34 (\hphantom{0}38\%) \\
        $\drsh$ Not recovered & 27 (52\%) & 29 (76\%) & 56 (\hphantom{0}62\%) \\
        & \\
        \textbf{Absent person-days} & \textbf{334 (52\%)} & \textbf{310 (48\%)} & \textbf{644 (100\%)} \\
        $\drsh$ Isolation & 109 (33\%) & 38 (12\%) & 147 (\hphantom{0}23\%) \\
        $\drsh$ Sickness & 95 (28\%) & 152 (49\%) & 247 (\hphantom{0}38\%) \\
        $\drsh$ Quarantine & 55 (17\%) & 5 (\hphantom{0}2\%) & 60 (\hphantom{00}9\%) \\
        $\drsh$ Other & 75 (22\%) & 115 (37\%) & 190 (\hphantom{0}30\%) \\
        & \\
        \textbf{COVID-19 cases} & \textbf{78 (19\%)} & \textbf{30 (13\%)} &  \textbf{108 (100\%)} \\
        $\drsh$ Confirmed & 25 (32\%) & 10 (\hphantom{0}33\%) & 35 (\hphantom{0}32\%) \\
        $\drsh$ Suspected & 53 (68\%) & 20 (\hphantom{0}67\%) & 73 (\hphantom{0}68\%) \\
        \bottomrule
    \end{tabular} 
\end{table}

@@

\begin{table}[!htpb]
    \centering
    \caption{\textbf{Analysis of molecular data}. Number of positive and negative saliva and airborne samples in each school.}
    \label{tab:molecular-data}
    \footnotesize
    \begin{tabular}{l rlrl p{.2cm} rlrl p{.2cm} rlrl}
    \toprule
    & \multicolumn{4}{c}{Saliva} & & \multicolumn{4}{c}{Air} & & \multicolumn{4}{c}{Air cleaner (HEPA filter)$^\dag$} \\ \cline{2-5} \cline{7-10} \cline{12-15} 
    & \multicolumn{2}{c}{School 1} & \multicolumn{2}{c}{School 2} & &  \multicolumn{2}{c}{School 1} & \multicolumn{2}{c}{School 2} & & \multicolumn{2}{c}{School 1} & \multicolumn{2}{c}{School 2} \\
    \midrule
    \textbf{Total} & \textbf{173} & & \textbf{89} & & & \textbf{68} & & \textbf{62} & & &  & &  & \\
    Negative & 160 & (\hphantom{0}92\%) & 81 & (\hphantom{0}91\%) & & 64 & (\hphantom{0}94\%) & 56 & (\hphantom{0}90\%) & &  & &  & \\  
    Positive & 13 & (\hphantom{00}8\%) & 8 & (\hphantom{00}9\%) & & 4 & (\hphantom{00}6\%) & 6 & (\hphantom{0}10\%) & & & &  & \\
    \midrule
    \textbf{Positive} & \textbf{13} & & \textbf{8} &  & & \textbf{4} & & \textbf{6} & & & \multicolumn{2}{l}{\textbf{2}}  & \multicolumn{2}{l}{\textbf{6}} \\
    SARS-CoV-2 & 12 & (\hphantom{0}92\%) & 7 & (\hphantom{0}88\%) & & 4 & (100\%) & 5 & (\hphantom{0}83\%) & & 2 & (100\%) & 4 & (\hphantom{0}66\%) \\
    Influenza & 1 & (\hphantom{00}8\%) & 0 & (\hphantom{00}0\%) & & 0 & (\hphantom{00}0\%) & 0 & (\hphantom{00}0\%) & & 0 & (\hphantom{00}0\%) & 1 & (\hphantom{0}17\%) \\
    Adeno & 0 & (\hphantom{00}0\%) & 1 & (\hphantom{0}12\%) & & 0 & (\hphantom{00}0\%) & 1 & (\hphantom{0}17\%) & & 0 & (\hphantom{00}0\%) & 1 & (\hphantom{0}17\%) \\
    \bottomrule
    \multicolumn{15}{l}{\scriptsize \emph{$\dag$: 20 swabs were taken from each filter at the end of the study period.}}
    \end{tabular}
\end{table}

\begin{figure}[!htpb]
    \centering
    \includegraphics{figures/molecular-descriptives.pdf}
    \caption{\textbf{Analysis of molecular data and comparison by study condition}. \textbf{(a)}~Proportion of positive airborne (solid line) and saliva (dashed line) samples (average per week). \textbf{(b)}~Viral concentration in positive airborne samples from BioSpot-VIVAS (average per week).}
    \label{fig:molecular-descriptives}
\end{figure}

@@

\begin{figure}[!htpb]
\centering
    \includegraphics[width=\linewidth]{figures/palas-descriptives.pdf}
    \includegraphics[width=\linewidth]{figures/palas-results.pdf}
    \caption{\textbf{Analysis of particle concentrations and comparison by study condition}. \textbf{(a)}~Boxplot of the daily average values for aerosol number concentration (CN in 1/cm$^3$) and particle mass concentration (PM for particles of sizes <1 to <10~$\mu$m, respectively in $\mu$gm$^{-3}$). Results for CO$_2$ and other environmental variables are shown in \supp~\zref{sec:detailed-palas}. \textbf{(b)}~Estimated reduction in aerosol number and particle mass concentrations with interventions (posterior mean as dot and 50\%-, 80\%- and 95\%-CrI as lines, respectively). }
    \label{fig:palas-results}
\end{figure}

@@

\begin{figure}[!htpb]
    \includegraphics[width=\linewidth]{figures/redcap-descriptives.pdf} 
    \includegraphics[width=\linewidth]{figures/redcap-results.pdf}
    \caption{\textbf{Analysis of epidemiological data and estimated transmission by study condition using Bayesian hierarchical transmission model}. \textbf{(a)}~Estimated mean cumulative number of cases for each school class after probabilistic simulation accounting for uncertainty in suspected cases and the date of symptom onset (\supp~\zref{sec:prob-sim}). Dotted red lines indicate the number of students per class. A comparison of the estimated number of new cases after probabilistic simulation with the observed number of new confirmed and suspected cases is shown in \supp~Fig.\zref{fig:redcap-supp-descriptives}. \textbf{(b)}~Estimated number of avoided infections associated with interventions across schools (posterior mean as dot and 50\%, 80\%, and 95\%-CrI as shaded areas) based on Bayesian hierarchical transmission model. Detailed estimation results are shown in \supp~\zref{sec:detailed-redcap}.}
    \label{fig:redcap-results}
\end{figure}

>>>>

\begin{table}[!htpb]
    \centering
    \caption{Overview of the study population, number of COVID-19 cases, and person-days of absences.}
    \label{tab:cases-overview-school}
    \footnotesize
    \begin{tabular}{l r r r}
    \toprule
         &  Class A & Class B & Total \\ \midrule 
        \textbf{Students} & \textbf{52 (58\%)} & \textbf{38 (42\%)} & \textbf{90 (100\%)} \\
        \emph{Gender} \\
        $\drsh$ Female & 20 (38\%) & 19 (50\%) & 39 (\hphantom{0}43\%) \\
        $\drsh$ Male & 32 (62\%) & 19 (50\%) & 51 (\hphantom{0}57\%) \\
        \emph{Vaccination status} \\
        $\drsh$ Vaccinated & 16 (31\%) & 11 (29\%) & 27 (\hphantom{0}30\%) \\
        $\drsh$ Not vaccinated & 36 (69\%) & 27 (71\%) & 63 (\hphantom{0}70\%) \\
        \emph{Recovery status} \\
        $\drsh$ Recovered last year & 25 (48\%) & 9 (24\%) & 34 (\hphantom{0}38\%) \\
        $\drsh$ Not recovered & 27 (52\%) & 29 (76\%) & 56 (\hphantom{0}62\%) \\
        & \\
        \textbf{Absent person-days} & \textbf{334 (52\%)} & \textbf{310 (48\%)} & \textbf{644 (100\%)} \\
        $\drsh$ Sickness & 95 (28\%) & 152 (49\%) & 247 (\hphantom{0}38\%) \\
        $\drsh$ Other & 75 (22\%) & 115 (37\%) & 190 (\hphantom{0}30\%) \\
        & \\
        \textbf{Respiratory cases} & \textbf{78 (19\%)} & \textbf{30 (13\%)} &  \textbf{108 (100\%)} \\
        $\drsh$ Epidemiological data & 25 (32\%) & 10 (\hphantom{0}33\%) & 35 (\hphantom{0}32\%) \\
        $\drsh$ Molecular data & 53 (68\%) & 20 (\hphantom{0}67\%) & 73 (\hphantom{0}68\%) \\
        \bottomrule
    \end{tabular} 
\end{table}

@@

\begin{figure}[!htpb]
    \centering
    \includegraphics{../../results/mol-data/descriptives.pdf}
    \caption{\textbf{Analysis of molecular data and comparison by study condition}. \textbf{(a)}~Proportion of positive airborne (solid line) and saliva (dashed line) samples (average per week). \textbf{(b)}~Viral concentration in positive airborne samples from BioSpot-VIVAS (average per week).}
    \label{fig:molecular-descriptives}
\end{figure}

@@

\begin{figure}[!htpb]
\centering
    \includegraphics[width=\linewidth]{../../results/env-data/particles-boxplot.pdf}
    \includegraphics[width=\linewidth]{../../results/env-data/estimation-results-figure.pdf}
    \caption{\textbf{Analysis of particle concentrations and comparison by study condition}. \textbf{(a)}~Boxplot of the daily average values for aerosol number concentration (CN in 1/cm$^3$) and particle mass concentration (PM for particles of sizes <1 to <10~$\mu$m, respectively in $\mu$gm$^{-3}$). Results for CO$_2$ and other environmental variables are shown in \supp~\zref{sec:detailed-palas}. \textbf{(b)}~Estimated reduction in aerosol number and particle mass concentrations with interventions (posterior mean as dot and 50\%-, 80\%- and 95\%-CrI as lines, respectively). }
    \label{fig:palas-results}
\end{figure}

@@

\begin{figure}[!htpb]
    \includegraphics[width=\linewidth]{../../results/epi-data/cases_by_week.pdf} 
    \includegraphics[width=\linewidth]{../../results/epi-data/avoided-infections.pdf}
    \caption{\textbf{Analysis of epidemiological data and estimated transmission by study condition using Bayesian hierarchical transmission model}. \textbf{(a)}~Estimated mean cumulative number of cases for each school class after probabilistic simulation accounting for uncertainty in suspected cases and the date of symptom onset (\supp~\zref{sec:prob-sim}). Dotted red lines indicate the number of students per class. A comparison of the estimated number of new cases after probabilistic simulation with the observed number of new confirmed and suspected cases is shown in \supp~Fig.\zref{fig:redcap-supp-descriptives}. \textbf{(b)}~Estimated number of avoided infections associated with interventions across schools (posterior mean as dot and 50\%, 80\%, and 95\%-CrI as shaded areas) based on Bayesian hierarchical transmission model. Detailed estimation results are shown in \supp~\zref{sec:detailed-redcap}.}
    \label{fig:redcap-results}
\end{figure}
